An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-20 poly-embed-journal/reviews/jmlr-response.tex
tweaks, pass
final edits for resubmission

In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
As such, they prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
To do so, they provide an alternate link construction to ours.
We therefore felt it important to highlight their work, so we added a new appendix section (\S~\ref{app:ccdim-construction}) to describe the connection, and added several references to it in context: footnote 1, just before Theorem~\ref{thm:thickened-separated}, and just before \S 7.1.

\bigskip
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.

    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    When the target prediction space is finite, one can always (translate and) scale up a consistent convex surrogate until it upper bounds the original loss.
    Thus, while the reviewer may be correct that Bayes risk matching implies that an embedding cannot itself be an upper bound, such as hinge loss embedding \emph{twice} 0--1 loss but not 0--1 loss itself, it can always be corrected to form an upper bound.

@@

    Yes, it does.
    We mention this fact informally following Construction 1; see margin note R2: D.

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
  We added a formal definition of consistency (Definition~\ref{def:consistency}).
  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
  We added a proof of Corollary~\ref{cor:poly-risk-fin-rep}, but did not include Proposition~\ref{prop:embed-bayes-risks} and~\ref{prop:embed-iff-trims-equal}, since these results are for a specific given discrete loss.

@@

	We thank the reviewer for the suggestion.  Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.  For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.  Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \url{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}.
	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.

>>>>

In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
As such, one can use their result to prove a slight generalization of our Theorem~\ref{thm:poly-ie-implies-consistent}.
We therefore felt it important to highlight their work, so we added a new appendix section (\S~\ref{app:ccdim-construction}) to describe the connection, and added several references to it in context: footnote 1, just before Theorem~\ref{thm:thickened-separated}, and just before \S 7.1.

\bigskip
\noindent
Best regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

    We added footnote 8 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point (margin note R2: B).
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    When the target prediction space is finite, one can essentially always (translate and) scale up a consistent convex surrogate until it upper bounds the original loss.
    Thus, while the reviewer may be correct that Bayes risk matching implies that an embedding cannot itself be an upper bound, such as hinge loss embedding \emph{twice} 0--1 loss (and not being an upper bound for twice 0--1 loss), it can typically be corrected to form an upper bound.

@@

    Yes; we mention this fact informally following Construction 1 (margin note R2: D).

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
  We added a formal definition of consistency (Definition~\ref{def:consistency}).
  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.
  On the $R_L$ notation for regret / excess risk, we see the confusion, and opted to use $\mathrm{Reg}_L$ to avoid ambiguity.
  We added a proof of Corollary~\ref{cor:poly-risk-fin-rep}, but did not include Proposition~\ref{prop:embed-bayes-risks} and~\ref{prop:embed-iff-trims-equal}, since these results are for a specific given discrete loss.

@@

	We thank the reviewer for the suggestion.  Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.  For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contributions of our paper are more salient in more complex settings.  Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \url{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}.
	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.
